Innovation and elaboration on the avian tree of life - supplementary materials

### 2023-06-01 Manuscript/supplementaries.tex
Update supplementaries.tex

>>>>

\begin{figure}[htbp]
\centering
   \includegraphics[width=0.7\textwidth]{Figures/InnovElabTree_supp_revision.pdf}
\caption{Avian phylogeny (n = 8748 species) showing distributions of species beak shape elaboration_{species} (inner circle, yellow scale), innovation_{species} (outer circle, blue scale), and Euclidean distance of species to the centroid of beak space (branches, cividis scale).}
\label{Fig:fig_phylogeny_supplement}
\end{figure}
